%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Senior Engineer} % Job title
    {Spotify Technology S.A.} % Organization
    {New York, NY} % Location
    {Apr. 2023 - Present} % Date(s)
    {
      \begin{cvitems} 
        \item {Build complex applications to support direct ad sales bringing in millions in revenue}
        \item {Design and build complex Java and Python backend services to support the ads business}
        \item {Create developer productivity tools and manage CI/CD pipelines}
        \item {Architect and communicate complex technical solutions to stakeholders}
        \item {Mentor junior developers and review pull requests}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Founder \& Lead Engineer} % Job title
    {Forcecode} % Organization
    {Remote} % Location
    {Nov. 2022 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Forcecode is a platform to help Salesforce developers get the job of their dreams through hands-on coding challenges}
      \end{cvitems}
    }

%---------------------------------------------------------
  % \cventry -- example with no body
  %   {Site Reliability Engineer} % Job title
  %   {Danggeun Market Inc.} % Organization
  %   {Seoul, S.Korea} % Location
  %   {Feb. 2021 - Mar. 2021} % Date(s)
  %   {
  %   }

%---------------------------------------------------------
  \cventry
    {Principal/Senior Engineer} % Job title
    {Slalom, Inc.} % Organization
    {Denver, CO} % Location
    {Apr. 2021 - Mar. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Act as a leader of the Digital Engagement (DE) team at Slalom}
        \item {SME of Salesforce Service Cloud and DE solutions}
        \item {Architect large-scale projects for clients in different verticals }
        \item {Build custom Lightning Web Components and Aura Components using advanced Apex logic}
        \item {Design integrations with external systems}
        \item {Build AI-enabled chatbot solutions across various Digital Engagement channels}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {WOW! Internet, Cable, \& Phone} % Organization
    {Denver, CO} % Location
    {Nov. 2020 - Apr. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Technical SME for the 2,000+ user org}
        \item {Responsible for architecting large-scale technical Salesforce projects}
        \item {Wrote a set of Apex coding standards and implemented a peer code review system for developers}
        \item {Responsible for overseeing the GitHub repository and approving pull requests}
        \item {Acted as go-to resource for maintaining complex SOAP and REST-based integrations with multiple external systems}
        \item {Created a sandbox refresh strategy to maintain integrity between pre-production environments}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Developer} % Job title
    {Youth Leadership Development Program} % Organization
    {Remote} % Location
    {May 2020 - Nov. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Lead developer responsible for engineering business solutions, coding back-end logic, and integrating Salesforce with external websites, leading to a 40\% increase in lead acquisition}
        \item {Ran training sessions on Flows for admins}
        \item {Automated business processes using Workflow Rules, Flows, Process Builder, and Apex classes/triggers}
        \item {Developed solutions by writing data models, BPMN flowcharts, user guides, and internal documents on student enrollment}
        \item {Collaborated with project manager and on/off-shore teams utilizing Agile methodologies}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
